Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2015-11-13 Paper/paper.tex
adding chirp mass bias plots

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How is PE affected by not including NS matter effects?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering 
% \textbf{BH-BH Injection; BH-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/NN_chirpMassBias_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; BH-BH Templates}
\includegraphics[width=1.7\columnwidth]{plots/TN_chirpMassBias_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; NS-BH Templates}
\includegraphics[width=1.7\columnwidth]{plots/TT_chirpMassBias_vs_SNR_q23.pdf}%\quad
\caption{These figures show the (fractional) difference between the chirp mass 
value corresponding to the median of its posterior probability distribution,
and the actual injected chirp mass,
as a function of the signal-to-noise-ratio (SNR) of the injected signal.
% In the top row, NS matter effects on the inspiral and merger waveform
% are neithed included in templates nor in the injected signal. 
In the top row, NS matter effects (inspiral and merger) are included in the
injections but not in templates. This corresponds to the current 
plan for aLIGO parameter estimation studies. The bottom row shows the effect
of additionally including NS matter effects in the templates.
% 
In each row, the left and right panel correspond to 
$q=m_\mathrm{BH}/m_\mathrm{NS}=\{2,3\}$, respectively. 
In each panel, the color of each curve corresponds to the value of NS 
deformability parameter $(\Lambda=\{500,1000,2000\})$, 
and line-style corresponds to the value of
the dimensionless spin on the BH ($\chi_\mathrm{BH}=\{-0.5,0,+0.5\}$).
}
\label{fig:TNT_chirpMassBias_vs_SNR_q23}
\end{figure*}
% 
\begin{figure*}
\centering 
% \textbf{BH-BH Injection; BH-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/NN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; BH-BH Templates}
\includegraphics[width=1.7\columnwidth]{plots/TN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
\textbf{NS-BH Injection; NS-BH Templates}
\includegraphics[width=1.7\columnwidth]{plots/TT_chirpMassCIWidth90_vs_SNR_q23.pdf}%\quad
\caption{These figures are similar to Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}
with the difference that here we show the width of the $90\%$ confidence 
interval (recovered) for chirp mass, as a function of the injected SNR. 
Note that the confidence interval's width is normalized by the injected
parameter value.
}
\label{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}
\end{figure*}
% 
\newpage
\newpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How is PE affected by not including NS matter effects?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure*}
% \centering 
% % \textbf{BH-BH Injection; BH-BH Templates}
% % \includegraphics[width=1.7\columnwidth]{plots/NN_chirpMassBias_vs_SNR_q23.pdf}\\ 
% \textbf{NS-BH Injection; BH-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TN_chirpMassBias_vs_SNR_q23.pdf}\\ 
% \textbf{NS-BH Injection; NS-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TT_chirpMassBias_vs_SNR_q23.pdf}%\quad
% \caption{These figures show the (fractional) difference between the chirp mass 
% value corresponding to the median of its posterior probability distribution,
% and the actual injected chirp mass,
% as a function of the signal-to-noise-ratio (SNR) of the injected signal.
% % In the top row, NS matter effects on the inspiral and merger waveform
% % are neithed included in templates nor in the injected signal. 
% In the top row, NS matter effects (inspiral and merger) are included in the
% injections but not in templates. This corresponds to the current 
% plan for aLIGO parameter estimation studies. The bottom row shows the effect
% of additionally including NS matter effects in the templates.
% % 
% In each row, the left and right panel correspond to 
% $q=m_\mathrm{BH}/m_\mathrm{NS}=\{2,3\}$, respectively. 
% In each panel, the color of each curve corresponds to the value of NS 
% deformability parameter $(\Lambda=\{500,1000,2000\})$, 
% and line-style corresponds to the value of
% the dimensionless spin on the BH ($\chi_\mathrm{BH}=\{-0.5,0,+0.5\}$).
% }
% \label{fig:TNT_chirpMassBias_vs_SNR_q23}
% \end{figure*}
% % 
% \begin{figure*}
% \centering 
% % \textbf{BH-BH Injection; BH-BH Templates}
% % \includegraphics[width=1.7\columnwidth]{plots/NN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
% \textbf{NS-BH Injection; BH-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TN_chirpMassCIWidth90_vs_SNR_q23.pdf}\\ 
% \textbf{NS-BH Injection; NS-BH Templates}
% \includegraphics[width=1.7\columnwidth]{plots/TT_chirpMassCIWidth90_vs_SNR_q23.pdf}%\quad
% \caption{These figures are similar to Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}
% with the difference that here we show the width of the $90\%$ confidence 
% interval (recovered) for chirp mass, as a function of the injected SNR. 
% Note that the confidence interval's width is normalized by the injected
% parameter value.
% }
% \label{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}
% \end{figure*}
% % 
\begin{figure*}
\centering 
\includegraphics[trim={{0.2\columnwidth} 0 0 0},width=2.1\columnwidth]{plots-TN/TN_MchirpBiases_Lambda_SNR.pdf}\\ 
\caption{These figures show the (fractional) difference between the chirp mass 
value corresponding to the median of its posterior probability distribution,
and the actual injected chirp mass,
as a function of the signal-to-noise-ratio (SNR) of the injected signal.
% In the top row, NS matter effects on the inspiral and merger waveform
% are neithed included in templates nor in the injected signal. 
In the top row, NS matter effects (inspiral and merger) are included in the
injections but not in templates. This corresponds to the current 
plan for aLIGO parameter estimation studies. The bottom row shows the effect
of additionally including NS matter effects in the templates.
% 
In each row, the left and right panel correspond to 
$q=m_\mathrm{BH}/m_\mathrm{NS}=\{2,3\}$, respectively. 
In each panel, the color of each curve corresponds to the value of NS 
deformability parameter $(\Lambda=\{500,1000,2000\})$, 
and line-style corresponds to the value of
the dimensionless spin on the BH ($\chi_\mathrm{BH}=\{-0.5,0,+0.5\}$).
}
\label{fig:TNT_chirpMassBias_vs_SNR_q23}
\end{figure*}
% 
\begin{figure*}
\centering
\includegraphics[trim={{0.4\columnwidth} 0 0 0},width=2.2\columnwidth]{plots-TN/TN_MchirpCIWidths90_0_Lambda_SNR.pdf}
\caption{These figures are similar to Fig.~\ref{fig:TNT_chirpMassBias_vs_SNR_q23}
with the difference that here we show the width of the $90\%$ confidence 
interval (recovered) for chirp mass, as a function of the injected SNR. 
Note that the confidence interval's width is normalized by the injected
parameter value.
}
\label{fig:TNT_chirpMassCIWidth90_vs_SNR_q23}
\end{figure*}
% 
\newpage
\newpage
